Sound Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-13 paper/paper.tex
nudge

\item Experiments obtained with our synthesiser show that the combination of
interval arithmetic to represent the controller coefficients and a two-stage
verification approach to continuously refine precision enables us to compute
a parametric, sound solution for $14$ out of $15$ digital stabilizing
controllers for a set of continuous and discrete plants with parametric
uncertainties.

>>>>

\item Experimental results with our synthesiser show that the
combination of interval arithmetic to represent the controller coefficients
and a two-stage verification approach to continuously refine precision
enables us to compute a parametric, sound solution for $14$ out of $15$
digital stabilizing controllers for a set of continuous and discrete plants
with parametric uncertainties.
